Dependent Object Types

### 2012-09-12 doc/candidacy/slides.tex
proposal

\input{macros}
\input{nuobj}

@@

@@

>>>>

\input{macros}
\input{nuobj}
\input{dot_macros}

@@

\begin{frame}{DOT: Status}
\begin{itemize}
\item basic calculus
\item type safety
\begin{itemize}
\item showed by counterexamples that subject reduction doesn't hold
\item sketch of plausible proof via logical relations
\end{itemize}
\item submission about this work-in-progress accepted to Foundations
  of Object-Oriented Languages (FOOL '12)
\item future work
\begin{itemize}
\item confirm proof of type safety and/or refine calculus
\item investigate translations of Scala features into DOT
\item implement a compiler front-end which uses DOT for typechecking
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{DOT: Syntax}
\begin{itemize}
\item terms
\begin{description}[method invocations]
\item[variables] $x$, $y$, $z$
\item[selections] $t.l$
\item[method invocations] $t.m(t)$
\item[object creations] $\new y c {t'}$\\
$c$ is a constructor $T_c \ldefs{\seq{l = v}\;\seq{m(x) = t}}$
\end{description}
\item types
\begin{description}[type intersections]
\item[type selections] $p.L$
\item[refinement types] $T \refine z {\seq D}$
\item[type intersections] $T \tand T'$
\item[type unions] $T \tor T'$
\item[a top type] $\Top$
\item[a bottom type] $\Bot$
\end{description}
\end{itemize}
\end{frame}

\begin{frame}[fragile]
\frametitle{DOT: Preservation Counterex. (Well-Formedness Lost)}
\center{// $y.A$ is not well-formed after $v$ is substituted for $x$.}
\begin{align*}
&\mlnew v {\Top \refine z {\Ldecl L \Bot {\Top \refine z {\Ldecl A \Bot \Top, \Ldecl B {z.A} {z.A}}}} \ldefs{}}{
\mlapp {\dotabs x {\Top \refine z {\Ldecl L \Bot {\Top \refine z {\Ldecl A \Bot \Top, \Ldecl B \Bot \Top}}}} {\\&\gap
\mlnew z {\Top \refine z {\ldecl l {\Bot \tfun \Top}}\mlldefs{\\&\gap\gap l = \dotabs y {x.L \tand {\Top \refine z {\Ldecl A {z.B} {z.B}, \Ldecl B \Bot \Top}}} {\\&\gap\gap\gap\dotabs a {y.A} {\app {(\dotabs x \Top x)} a}}}}{
\ \app {(\dotabs x \Top x)} z
}}}{\ v}}
\end{align*}
\end{frame}
